---
title: "williamdavis"
author: "William Davis"
date: "4/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create a dataframe of your bag including the following
  - Name of each club
  - Average distance for each shot
  - trajectory 

```{r Create Bag}

```

## Create a handicap
  - The handicap system gives players a measurment for how well they should be scoring
  - The system is on a rating of 0-36 with better players having lower numbers
    - Going below 0 is possible but is only for extremly talented golfers
    - This number would then be considered to be a +(Handicap)
  - Your handicap is the rating at which youve played the last 10 Games
 

```{r Generate Handicap}

```

## Course handicap and target score
  - Each course is given a rating and a slope to the par for the course
  - Rating is how well a scractch golfer should play
    - Scratch is 0 handicap
    - Easier courses have a lower rating and a harder courses have a higher rating
  - Slope is how well a bogey gofler should should play
    - This is a rating for how condtions may affect higher handicap players
    - A bogey golfer is someone who is averaging around one stroke over par per hole
    - Same characteritics of diffculty for Rating apply to Slope
  - A course handicap takes into account the difficutly of the course and your handicap
  - The course handicap plus par is the target score for the round
    


```{r Generate Course Handicap}

```

## Club to hit and target
  - There are many factors that go into hitting each type of shot (Wind, shot shape, hazards)
  - Ideally the golfer should know distance to hazards are 
  - They should also know what shot shape they are going to hit
    - Experienced golfers can choose their shot shape with practice
      - Fade: starts straight and funnels right towards end
      - Draw: starts stright and funnels left at end
    - Most amateur golfer will hit one type of shot shape without intention
  - Wind coupled with trajectory will affect how far the ball will travel both in distance and laterally 
  - Trajectory will not be used for closer shots where full swings are not used


```{r}

```

